Architectures and Open pNets

### 2018-11-06 2018-Arch-pNets/arch-pNets.tex
define underlined actions + WOT lemma V2

\begin{example}\emph{An open-transition.}
  \label{OT:enable-composed}
  The \texttt{EnableCompL} pNet of Fig. \ref{schema:enable-composed} has 2 controllers 
  and 2 holes. One of its possible open-transition is:

 \smallskip
 $  OT_2  = \openrule{ 
							(P\mapsto \delta(x4), Q\mapsto accept(x4))               
%                            \xrightarrow{\delta(x4)}_P ~~
%                            \xrightarrow{accept(x4)}_Q 
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {A1_0 \OTarrow{\underline{\delta(x4)}} A1_1}
  $\noteSB{The underline notation did not appear until here.}
\end{example}

>>>>

\begin{example}\emph{An open-transition.}
  \label{OT:enable-composed}
  The \texttt{EnableCompL} pNet of Fig. \ref{schema:enable-composed} has 2 controllers 
  and 2 holes. One of its possible open-transition is\footnote{Note the underlined action notation that we use to represent synchronised actions, i.e. actions that are the result of a synchronisation and that we declare as \emph{non-observable}. Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector. This allows us to define a weak bisimilarity equivalence with p=compositional properties.}: 
\noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}

 \smallskip
 $  OT_2  = \openrule{ 
							(P\mapsto \delta(x4), Q\mapsto accept(x4))               
%                            \xrightarrow{\delta(x4)}_P ~~
%                            \xrightarrow{accept(x4)}_Q 
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {A1_0 \OTarrow{\underline{\delta(x4)}} A1_1}
  $
\end{example}
